\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[top=1cm, bottom=1cm, left=1.25in, right=1.25in]{geometry}
\usepackage{dcolumn}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage[dvipsnames]{xcolor}
%% Title settings
\titleformat{\section}[block]{\Large\bfseries\filcenter}{}{1em}{}
\titlespacing*{\section}{0pt}{0.1cm}{0.1cm}
\titlespacing*{\subsection}{0pt}{0.1cm}{0.1cm}

\definecolor{light-gray}{gray}{0.35}

\titleformat{\section}
{\color{BrickRed}\normalfont\Large\bfseries}
{\color{BrickRed}\thesection}{1em}{}

%% List settings
\renewcommand{\labelitemi}{$\circ$}
\renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemiii}{$\circ$}
\renewcommand{\labelitemiv}{$\circ$}

%% Link settings
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}

%% Makes the '+' in the phone number smaller
\def\Plus{\texttt{+}}
\def\Minus{\texttt{-}}

%% Suppress page numbering
\pagenumbering{gobble}


\begin{document}
\begin{minipage}{0.6\textwidth}
	\Huge
	Bryce Lackenby
	\vspace{0.5cm}
	\normalsize
	\\
	Data Scientist, Data Analyst, Machine Learning Engineer
\end{minipage}
\vspace{0.5cm}
\noindent
\begin{minipage}{0.6\textwidth}
  \small
	Sydney, NSW \\
	Email: brycelackenby@gmail.com \\
	Phone: \Plus61 466 611 869 \\
	Github: \href{https://github.com/lackos/}{github.com/lackos/} \\
	GitLab: \href{https://gitlab.com/BGCLack/}{gitlab.com/BGCLack/} \\
	LinkedIn: \href{https://www.linkedin.com/in/bryce-lackenby/}{linkedin.com/in/bryce-lackenby/}
\end{minipage}
% \vspace{0.5cm}
\rule{16.6cm}{0.1cm}
\section*{Education}
PhD (Theoretical Physics) \hfill $2016-2019$ \\
\textit{UNSW Sydney} \\
\textit{Nuclear and Atomic Physics} \\
\linebreak
Graduate Certificate in Mathematics \hfill $2015$ \\
\textit{UNSW Sydney} \\
\linebreak
Bachelor of Advanced Science (Mathematical Physics) \hfill $2011-2014$ \\
\textit{UNSW Sydney} \\
\textit{First Class Honours}

\section*{Experience}
\subsection*{PhD}
\textcolor{light-gray}{January 2016 - October 2019}
\begin{itemize}
	\item Contributed to numerical code to model complex atomic systems (Fortran 95).
	\item Developed a PostgreSQL schema to store numerical results for future queries and analysis.
	\item Wrote python scripts to automate the implementation of the numerical code and upload results to a PostgreSQL database.
  \item Wrote python scripts to construct informative visualizations of data for publication.
\end{itemize}
\subsection*{Lowes}
\textcolor{light-gray}{October 2019 - January 2020}
\begin{itemize}
	\item Wrote python scripts to clean and visualize financial data for business development.
  \item Developed models to optimize the financial costs of the company.
\end{itemize}
\subsection*{Postgraduate Dental School}
\textcolor{light-gray}{(Casual) January 2020}
\begin{itemize}
  \item Scraped and cleaned web data with bash and python scripts. Programmed a bot (in python) to use the data in email marketing campaign.
\end{itemize}
\section*{Technical Skills}
\begin{minipage}[t]{0.6\textwidth}
  \subsection*{Programming}
  Python \\
  \-\hspace{0.5cm} \textcolor{light-gray}{Pandas, PySpark, Django, TensorFlow, scikit\_learn \\
  \-\hspace{0.5cm} Keras} \\
  BASH \\
  C \\
  R \\
  SQL \\
  \-\hspace{0.5cm} \textcolor{light-gray}{PostgreSQL, MySQL} \\
  Fortran 95 \\
  HTML \& CSS \\
  Git
\end{minipage}
\begin{minipage}[t]{0.6\textwidth}
  \subsection*{Analytical}
  Data Manipulation \\
  Data Visualization \\
  Feature Engineering \\
  Statistics and Probability \\
  Neural Networks\\
  Excel \\
  \subsection*{Professional}
  Technical Writing \\
  Public Presentations \\
  Explaining high level concepts
\end{minipage}

\end{document}
